\documentclass[a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb,mathrsfs}
\usepackage{graphicx}
\usepackage[font=small]{caption} % Without options this makes it so the stray : is removed for figures with empty captions.
% \graphicspath{{./figures/}}

\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}
\bibliographystyle{alpha}



\usepackage{tikz}
% \usetikzlibrary{}
% \usetikzlibrary{decorations.pathmorphing} % For wiggly lines
% \usetikzlibrary{decorations.markings} % For mid-line arrows
% \usetikzlibrary{arrows.meta} % For more arrow options


% Todo stuff:
\usepackage{todonotes}
\presetkeys{todonotes}{size=\small}{}

% Theorems | Props | Defs | Etc share a counter:
\newtheorem{counter}{Counter}[section]
\newtheorem{definition}[counter]{definition}
\newtheorem{theorem}[counter]{theorem}
\newtheorem{proposition}[counter]{proposition}
\newtheorem{lemma}[counter]{lemma}
\newtheorem{remark}[counter]{remark}
\newtheorem{corollary}[counter]{corollary}

% Blackboard Bold Shortcuts
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}


% Looks like \mathbb{1}
\newcommand{\idty}{\mathrm{1}\mkern-4mu{\mathchoice{}{}{\mskip-0.5mu}{\mskip-1mu}}\mathrm{l}}

% Operators
\DeclareMathOperator{\Tor}{Tor}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Rep}{Rep}


% My research shortcuts
% Building blocks
\newcommand{\overarrowsplus}{\raisebox{-.6ex}{\tikz[{To[sharp]}-,scale=.3]{	\draw (0,1) -- (1,0);\draw[white,-,line width= 3pt] (1,1) -- (0,0);	\draw (1,1) -- (0,0);}}}
\newcommand{\overarrowsminus}{\raisebox{-.6ex}{\tikz[{To[]}-,scale=.3]{	\draw (1,1) -- (0,0);\draw[white,-,line width= 3pt] (0,1) -- (1,0);	\draw (0,1) -- (1,0);}}}
\newcommand{\downcurvearrowleft}{\raisebox{1ex}{\scalebox{-1}{$\curvearrowright$}}}
\newcommand{\downcurvearrowright}{\raisebox{1ex}{\scalebox{-1}{$\curvearrowleft$}}}

%opening
\begin{document}
\noindent{\large\bf Project Description \hfill Count Me In 2025}
\vspace{1cm}

\section*{Overview}
This project asks what types of functions can appear in (certain well behaved) \emph{representations of quantised enveloping algebras of Lie superalgebras}.
Specifically, do these functions have strong enough recursive behavior to qualify as \emph{q-holonomic functions}?

We're motivated by the fact that these representations can be used to make quantum knot invariants, whose q-holonomicity is closely linked to the role they play in physics.
Lie superalgebras are particularly interesting because they appear in recent constructions of physical theories known as Chern-Simons theories \cite{Mikhaylov_Witten_2015}.

\subsection*{Main References:}

\begin{description}
  \item[Lie Superalgberas:] We will focus on $\mathfrak{sl}(n|m)$ for $n \neq m$, and on specifically their typical representations.
    \begin{itemize}
      \item The classic references are \cite{Kac1977,Kac_1978}.
      \item For a textbook, see \cite{Musson_2012}.
    \end{itemize}
  \item[The Quantum Group $U_h\mathfrak{sl}(n|m)$] - we will focus on representations that come from those of $\mathfrak{sl}(n|m)$, but need the \emph{quantum Serre relations} involving $q = e^{h/2}$ that appear in the quantisation in order to get interesting $q$-holonomic functions.
    \begin{itemize}
      \item Introduced in \cite{Yamane_1994}, see especially Theorem 10.5.1 for a presentation.
      \item See also \cite{Geer_2006}, and \cite[\S 3.3]{Geer_2007} for some more brief treatments.
      \item A textbook for the non-super case is \cite{Lusztig_2010}.
      \item See \cite[Theorem 1.2]{Geer_2007} for the relationship between $\mathfrak{sl}(n|m)$ and $U_h \mathfrak{sl}(n|m)$ representations.
      \item For a in depth look at $\mathfrak{sl}(2|1)$, see \cite{Brown_Geer_2024}.
    \end{itemize}

  \item[q-Holonomic Systems:]
  We'll want to use the closure properties.
    \begin{itemize}
     \item A good survey is \cite{Garoufalidis_Le_2016}.
     \item The classic is \cite{Sabbah_1993}, but it's in french. 
     \item For the $\mathfrak{sl}(2|1)$ version, there's \cite{Brown_Geer_2024}.
     \item For a proof of q-holonomicity for the coloured Jones polynomial, there's \cite{Garoufalidis_Le_2005}.
  \end{itemize}
\end{description}

\section*{Details}

We will focus on \emph{typical representations} of the classical lie superalgebra $\mathfrak{sl}(n|m)$, where $n \neq m$.
These have standard deformations to $U_h\mathfrak{sl}(n|m)$ representations and are classified up to isomorphism by a tuple of complex parameters $(a_1,\ldots,a_{m+n+1})$ which must satisfy the following set of linear inequalities:
\begin{equation}
  a_{m+1} \neq \sum_{k=m+2}^j a_k - \sum_{\ell = 1}^m a_\ell -2m - 2 + i + j
\end{equation}
for $i = 1,\ldots,m+1$, $j = m+1,\ldots, m+n+1$, see \cite[Example 1, pg 620]{Kac_1978}.

The parameters $a_k$ are called the \emph{weights} of the associated representation $V(\overline{a})$, which is characterised by having a \emph{highest weight vector} $v \in V(\overline{a})$ such that
\begin{equation}
    h_k v = a_k v, \quad\text{ and }\quad E_k v = 0  \quad\text{for } k = 1,\ldots,m+n+1.
\end{equation}

\section*{Process:}
\begin{itemize}
  \item We want to describe the associated $U_h\mathfrak{sl}(n|m)$-representations in terms of explicit matrices (which will depend on the parameters $n,m$ and $a_k$.)
  \item Then we want to prove that the coefficients of those matrices are q-holonomic functions.
  \item We'd like to also understand if the $R$-matrix has q-holonomic coefficients.
\end{itemize}



\bibliography{\jobname.bib}

\end{document}

